\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
checked edits and comments all the way to sec V

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2007, six of the competing teams completed the 96km course set for the DARPA
Urban Challenge In 2004, the farthest distance traveled by a vehicle
autonomously in the DARPA \cite{spectrumUrbanChallenge2007}. They did so while
obeying the traffic laws followed by human drivers, navigating along with other
moving vehicles, and following correct intersection precedence order. Since
then, Google's driverless cars have clocked more than 250,000km on public roads
in urban California, USA \cite{tedThrun2011}. In 2010, researchers from the
University of Parma successfully completed an autonomous
\textit{intercontinental} run from Parma, Italy to Shanghai, China
\cite{cnnVislab2010}. The successful completion of all these milestones
suggests that autonomous cars are here to stay, and are ever closer to becoming
commercially available. With the arrival of autonomous cars, it also becomes
possible to optimize traffic in ways not possible for human drivers. 
%\commentd{If we need space, I agree with Dr Chiu, some of this could be
%trimmed}

@@

\begin{figure}[t]
  \centering \includegraphics[width=\linewidth]{downtown_atx.png}
  \caption{A simulation of autonomous agents in downtown Austin, Texas, as visualized through the UI available within the AORTA simulator}
  \label{fig:ui_screenshot}
  \vspace{-15pt}
\end{figure}

>>>>

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2007, six of the competing teams completed the 96km course set for the DARPA
Urban Challenge \cite{spectrumUrbanChallenge2007}. They did so while
obeying the traffic laws followed by human drivers, navigating along with other
moving vehicles, and following correct intersection precedence order. Since
then, Google's driverless cars have clocked more than 250,000km on public roads
in urban California, USA \cite{tedThrun2011}. In 2010, researchers from the
University of Parma successfully completed an autonomous
\textit{intercontinental} run from Parma, Italy to Shanghai, China
\cite{cnnVislab2010}. The successful completion of all these milestones
suggests that autonomous cars are here to stay, and are ever closer to becoming
commercially available. With the arrival of autonomous cars, it also becomes
possible to optimize traffic in ways not possible for human drivers. 
%\commentd{If we need space, I agree with Dr Chiu, some of this could be
%trimmed}

@@

\begin{figure}[t]
  \centering \includegraphics[width=0.9\linewidth]{downtown_atx.png}
  \caption{A simulation of autonomous agents in downtown Austin, Texas, as visualized through the UI available within the AORTA simulator}
  \label{fig:ui_screenshot}
  \vspace{-20pt}
\end{figure}
